A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-05-20 manuscript.Rmd
cite FAIR principles close #18

<!-- Hands-on: check changed hash -->
A prerequisite to reproducibility is the permanent availability of both code and data [@akhlaghi2020towards].
We use containers to guarantee that all code components are available and work as expected.
Ideally, all data are also stored well documented [@codebook] in the repository [for a more comprehensive argument for publishing data see @vanlissa2020worcs], but this is not always feasible.

@@

```{r, include=FALSE}
knitr::write_bib(c(.packages(), "rticles", "gert", "bookdown", "lavaan", "knitr", "targets", "renv", "tidyverse"),
                 "packages.bib")
```

>>>>

<!-- Hands-on: check changed hash -->
A prerequisite to reproducibility is the permanent availability of both code and data [@akhlaghi2020towards].
We use containers to guarantee that all code components are available and work as expected.
Ideally, all data are also stored well documented [@codebook] in the repository following the FAIR principles [@wilkinsonFAIRGuidingPrinciples2016].
We believe that sharing data is highly beneficial for the research community [for a more comprehensive argument for publishing data see @vanlissa2020worcs], but this is not always feasible.

@@

```{r, include=FALSE}
knitr::write_bib(c(.packages(), "here", "rticles", "gert", "bookdown", "lavaan", "knitr", "targets", "renv", "tidyverse"),
                 "packages.bib")
```
